netcdf_to_brick_projected

### 2018-10-22 src/biological_data_prep.Rmd
feck all progress :(

>>>>

#add columns for the env. variables
The ones ypu have to add are...

mlp
salinty_1
salinity_depth
ssh
temp_1
temp_depth
chl_1
chl_depth
o2_1
o2_depth

populate the columns with NA
```{r}
data_aea$mlp <- NA
data_aea$salinty_1 <- NA
data_aea$salinity_depth <- NA
data_aea$ssh <- NA
data_aea$temp_1 <- NA
data_aea$temp_depth <- NA
data_aea$chl_1 <- NA
data_aea$chl_depth <- NA
data_aea$o2_1 <- NA
data_aea$o2_depth <- NA
write.csv(data_aea,"../output/bio/data_aea_cell_amo_nao_bins_env.csv", row.names = FALSE)
```

### 2018-10-22 src/netcdf_to_brick_projected.Rmd
feck all progress :(

```{r pre-install packages, message=FALSE}
packages <- c("ncdf4")
source("../src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

maybe start by splitting the occurence data into year-month? Then you can search for the rasters without going through everything....
```{r}
species_obs_date <- split(data_aea,paste(data_aea$year, data_aea$month))
species_obs_date
```

>>>>

```{r pre-install packages, message=FALSE}
packages <- c("ncdf4", "sp")
source("../src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

@@

maybe start by splitting the occurence data into year-month? Then you can search for the rasters without going through everything....
```{r}
library(sp)
species_obs_date <- SpatialPointsDataFrame(coords = xy, data = data_aea, proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")) #convert into a spatialpoints dataframe to do the extraction
species_obs_date <- spTransform(species_obs_date, CRS = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs") #need to reproject.... note -60 used to be -91. Changed to 'straighten up'
split_obs <- split(species_obs_date, paste(species_obs_date$year, species_obs_date$month))
```

just check the species_obs_date complete file in a plot
```{r}
plot(species_obs_date)
```
looks good...

```{r}
for(i in split_obs){
  print(i)
}
```

hmm what now....

You want to populate the following fields in the species_obs_date spatialdf
mlp
salinty_1
salinity_depth
ssh
temp_1
temp_depth
chl_1
chl_depth
o2_1
o2_depth

where _1 indicates the surface layer [[1]] and depth is == depthlayerno
Note mlp and ssh have only one single layer ([[1]])

netcdf_list = list of all netcdfs
no_netcdf = number of netcdfs created
netcdf_name = name of netcdfs - will match the name of the raster bricks too.

```{r}

```
